### 2015-09-29 untitled.tex
edited untitled.tex

Figure \ref{fig:example} is the resulting schedule by using the period enforcer algorithm. The first job of task $\tau_2$ arrives at time $0$ is executed as if there is no period enforcer. The second job of task $\tau_2$ requires some attention to understand how the period enforcer algorithm works. Note that the first computation segment of task $\tau_2$ does not suffer from any deferrable execution (it is postponed due to higher-priority block). Therefore, it is always placed to the ready queue and scheduled as early as possible.

Let's now look at the computation segment $C_2^2$ of the second job of task $\tau_2$. This segment is placed back to the ready queue at time $19$. If there is no period enforcer, this computation segment should be executed from $19$ to $20$. However, the period enforcer algorithm intentionally defers this computation segment to ensure \emph{the periodic behaviour} of the computation segment $C_2^2$. Therefore, this computation segment is \emph{activated} to the ready queue at time $9+T_2=9+11=20$. This results in a deadline miss.

>>>>

Figure \ref{fig:example} is the resulting schedule by using the period enforcer algorithm. The first job of task $\tau_2$ (that arrives at time $0$) is executed as if there is no period enforcer. The second job (that releases at time $11$) of task $\tau_2$ requires some attention to understand how the period enforcer algorithm works. Note that the first computation segment of task $\tau_2$ does not suffer from any deferrable execution (it is postponed due to higher-priority block). Therefore, it is always placed to the ready queue and scheduled as early as possible.

Let's now look at the computation segment $C_2^2$ of the second job of task $\tau_2$. This segment is placed back to the ready queue at time $19$ after its self-suspension. Without period enforcer, this computation segment should be executed from $19$ to $20$. However, the period enforcer algorithm intentionally defers this computation segment to ensure \emph{the periodic demand} of the computation segment $C_2^2$. Therefore, this computation segment is \emph{activated} to the ready queue at time $9+T_2=9+11=20$. This results in a deadline miss.\footnote{By using the notations of \cite{Raj:suspension1991}, $ET_{2,1}^2=9, ET_{2,2}^2 = \max\{9+11, 19\}=20$.}
